Rank Recovery

### 2020-11-10 output_scripts/rank_recovery.Rmd
add file to sim ranks and compare

We first simulate a single dense network from the C-MMHP model.

@@

@@

stansims <- rstan::extract(stanfit)
## truth is .1, .2, .4, .7, .9
apply(stansims$f, 2, mean)
apply(stansims$f, 2, sd)

# most important is the order
m3_rank <- order(apply(stansims$f, 2, mean))
#order(apply(stansims$f, 2, sd))
```

```{r fit I&SI}
count_data <- get_wl_matrix(df = cbind(clean_sim_data$start,clean_sim_data$end))
isi.out <- compete::isi98(m = count_data, random = TRUE)
isi_rank <- as.numeric(rev(isi.out$best_order)) # ranked from lowest to highest

isi_rank
true_rank <- c(1:5)

@@

# most important is the order
m3_dc_rank <- order(apply(stansims_dc$f, 2, mean))
```

@@

>>>>

We first simulate a single dense network from the C-MMHP model,
with a latent rank vector given by

$$
f =(0.1, 0.2, 0.4, 0.7, 0.9).
$$

@@

We can then extract the posterior mean rank from our fitted model.

@@

stansims <- rstan::extract(stanfit)
## truth is .1, .2, .4, .7, .9

apply(stansims$f, 2, mean)
# posterior mean
# posterior sd
# apply(stansims$f, 2, sd)

# most important is the order
m3_rank <- order(apply(stansims$f, 2, mean))
#order(apply(stansims$f, 2, sd))
```
We can compare this to the ranking from I&SI on the count data alone, which
is given below.

```{r fit I&SI, results='hide'}
count_data <- get_wl_matrix(df = cbind(clean_sim_data$start,clean_sim_data$end))
isi.out <- compete::isi98(m = count_data, random = TRUE)
isi_rank <- as.numeric(rev(isi.out$best_order)) # ranked from lowest to highest
```
```{r print isi result}
isi_rank
```

Similarly we can compare these and the true ranking pairwise.

```{r}
true_rank <- c(1:5)

@@

# most important is the order
m3_dc_rank <- sort(apply(stansims_dc$f, 2, mean))
```

@@

# Extrapolation from inferred rank on subset

We also wish to consider how well we can infer the latent rank 
over time, where
